Cauchy example

### 2020-08-28 src/s_cauchy.Rmd
ben run through and sent to Aki

g <- c_df %>% 
  melt(id.vars=c("source", "iter")) %>% 
  mutate(source=if_else(source=="split-Rhat", "Split-Rhat", as.character(source))) %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(bins=50, position="identity", alpha=0.8) +
  scale_fill_grey("Parameterisation", labels=c("Nominal", "Alternative")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  facet_wrap(~source+iter, scales="free") +
  scale_x_continuous(limits=my_lims) +
  theme(strip.text = element_text(size=14, colour="black"),
        axis.text = element_text(size=12, colour="black"),
        axis.title = element_text(size=14, colour="black"),
        legend.text = element_text(size=14, colour="black"),
        legend.title = element_text(size=14, colour="black")) +
  xlab("Value")

>>>>

g <- c_df %>% 
  melt(id.vars=c("source", "iter")) %>% 
  mutate(source=if_else(source=="split-Rhat", "Split-Rhat", as.character(source))) %>% 
  mutate(iter=fct_relevel(as.factor(iter), "1000", "10,000")) %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(bins=50, position="identity", alpha=0.8) +
  scale_fill_grey("Parameterisation", labels=c("Nominal", "Alternative")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  facet_wrap(~iter+source, scales="free") +
  scale_x_continuous(limits=my_lims) +
  theme(strip.text = element_text(size=14, colour="black"),
        axis.text = element_text(size=12, colour="black"),
        axis.title = element_text(size=14, colour="black"),
        legend.text = element_text(size=14, colour="black"),
        legend.title = element_text(size=16, colour="black")) +
  xlab("Value")
